{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-09-09 wacv_for_review.tex
Last stretch. This draft is ready to submit.

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. This is primarily because
most of embedded systems come with an image acquisition pipeline, and
a tremendous amount of progresses on computer vision research has been
made for the past few decades. However, to successfully deploy a
computer vision algorithm on any existing embedded systems, a vision
algorithm needs to satisfy, at least, two criteria with the assumption
of reasonably good performance: minimal, manual intervention after
deployment and small footprint of consuming computational
resources. While these criteria kept in mind, to develop a single,
target tracking system, we propose an ensemble of the kernelized
correlation filters (KCF), we call {\it E}nKCF. This committee of KCFs
is specifically designed to address the scale-change and dynamic
maneuver of the target over frames. In particular, to guarantee a
high-speed, run-time performance, we deploy each of KCFs in turn. We
also developed a Bayes filter to minimize any potential drifts between
individual KCFs' transitions. Experimental results showed that the
performance of ours are, on average, 70.10\% for precision at 20
pixels, 53.00\% for success rate for OTB100 data, and 54.50\% and
40.2\% for UAV123 data. These results showed that our method is better
than existing ones over 5\% on precision on 20 pixels and 10-20\% on
AUC on average. Moreover our implementation ran at 340 fps for OTB100
and at 416 fps for UAV123 data that is faster than DCF (292 fps) for
OTB100 and KCF (292 fps), DCF (457 fps) for UAV123. To increase
flexibility of the proposed {\it E}nKCF running on various one-chip
computer, e.g., one with GPUs, we explored different levels of deep
features.
\end{abstract}

@@

\begin{figure*}[!h]
\centering
\begin{tabular}{cc}
\includegraphics[width=14.00cm]{./figures/Workflow_MKCF+PF.pdf}\\
\end{tabular}
\caption{The work-flow of {\it E}nKCF tracking algorithm. We show the
  first seven frames of tracking where the first frame is the
  initialization frame. Afterward, the order of deploying three KCFs
  is repeating.}
\label{Workflows}
\end{figure*}

One of the dominant frameworks for online, object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that a target location is given at the beginning
like any other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a form of the
circulant matrix \cite{henriques2015high}. One can optimally solve
this regression problem using a ridge regression in a closed
form. However, this solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, an object tracking pipeline based on the
correlation filter can run very efficiently and be even easily
implemented. In fact, an extension of a linear correlation filter, the
kernelized correlation filter with multi-channel features
\cite{henriques2015high} showed impressive object tracking results and
outperformed other state-of-the-art tracking algorithms in terms of
run-time and tracking accuracy. However, a vanilla form of such an
online tracker is prone to drift, and fails to track a target over a
long period of time \cite{henriques2015high}. This is primarily due to
the dilemma of stability-plasticity in updating appearance model,
where the appearance model will be overfitted to only the images used
to train, unless a compromise on the frequency of updating the model
is carefully implemented \cite{santner2010prost}. For example, one may
handle a target's scale variation by just concatenating multiple
correlation filters including KCF and running them on each
frame. Alternatively one could think of scanning the region of
interest (ROI) with a list of templates in predefined scale ratios to
find the target in appropriate scale
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
these approaches will drastically reduce run-time performance because
they are proposed to run multiple KCF on each frame.

Another way of handling the scale change for the correlation filter
based approach is to estimate a correct scale at a location where a
target highly likely appears \cite{zhang2014fast} -- estimate a
target's translation first and estimate a correct scale afterward. In
particular, Zhang and his colleagues use the MOSSE tracker to estimate
a target's translation. And then they attempted to update the scale of
the target by further analyzing image, sub-regions with high
confidence. This is based on an assumption that the scale of a target
would not change much over two consecutive frames. Similarly, Ma and
his colleagues used two KCFs to learn the translation and scale of a
target separately \cite{ma2015long}. In particular, a KCF is used to
learn the translation of the target and its background. Given this,
another KCF is used to learn the target area to estimate a new scale
of the target. However, because of running more than a KCF on each
frame, this method degrades its run-time performance (i.e., $\leq 50
fps$). Our method is motivated by this idea -- the idea of deploying
multiple KCFs to address the issues of single target tracking: scale
and translation, but in a more efficient way. Figure \ref{Workflows}
illustrates the work-flow of the {\it E}nKCF. In particular, to
maximize run-time performance and accuracy, instead of running them
all together on every frame, we deploy three KCFs in turn:
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). By doing so, our method aims at addressing a scale
change and estimate target's motion efficiently while maintaining or
increasing run-time performance.

The contribution of this paper is a novel, single-target tracking
algorithm running in a very high-speed, $\geq 300$ fps that deploys an
ensemble of KCFs, in turn, to more effectively address the scale
variance and the dynamic maneuver of a target while preserving
run-time performance as high as possible. We also developed a Bayes
filter to minimize any potential drifts while transiting one KCF to
another. In addition, we explore deep features with varying levels of
abstraction in the proposed {\it E}nKCF to improve tracking
performance and increase its flexibility being deployed on high-end,
one-chip computer with GPUs.

@@

In this paper, we propose a novel way of utilizing a multiple of the
KCFs \cite{henriques2015high} to effectively handle scale variations
and dynamic maneuvers of a target. To maintain or improve the run-time
performance of the original KCF (e.g., $\ge$ 300), we deploy three
KCFs in turn, instead of applying them on the same image frame
together. Each of these KCFs is designed to address specific
challenges, i.e., scale and translation. By alternating their
deployments, our algorithm will improve the performance of the
original KCF while preserving the efficient nature and small-footprint
of the KCF computation.

@@

Since Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high} on VOT15
challenge \footnote{\url{http://www.votchallenge.net/vot2015/}}, many
variation of KCF were investigated. For example, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is similar to that of \cite{ma2015long} in
that more than one KCF is used to address the challenges of single
target tracking. But ours is different from their approach because we
do not use those multiple KCFs together at every frame, but
alternatively at every $k$ frame. It intuitively makes sense to
alternatively use multiple KCFs with different purposes because the
appearance of a target does not change drastically over consecutive
image frames. For most case, even it looks the appearance changes,
learning a correlation filter over consecutive frames would not be
much different from the one learned using the image few or $k$ frames
later. Figure \ref{fig:Filters_Comparison} shows examples supporting
this observation.

@@

The algorithm \ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF.
The order of running these three KCFs is important because each of
these filters aims at addressing different challenges; The
\textit{target+large background} translation filter, $R_{t}^{L}$, is
applied to the $i$th and $i$+$1$th image frames, another translation
filter, $R_{t}^{S}$ is applied to the $i$+$2$th and $i$+$3$th image
frames, and then the scale filter, $R_{s}$ is applied to the $i$+$4$the
image. This order repeats until the end of the image frames. The
translation filter, $R_{t}^{L}$, is intended to run right after the
scale filter, $R_s$, runs which is applied at every other $i$+$4$
frames. We run these filters in this way because we want to minimize
any drifts that are likely to happen running only $R_{s}$. In
addition, the filter, $R_{t}^{S}$, is applied to every other two
frames before $R_{s}$ and right after two consecutive frames running
$R_{t}^{L}$. By repeating this order of learning KCFs, we can
integrate more discriminative shape features that cannot be learned by
$R_{t}^{L}$. This is because it incorporates a large area about
background in the learned model. The filter, $R_{t}^{L}$, uses shape
and color information together to recover from any potential drifts --
drifts could happen only looking the target's scale by the filter,
$R_{s}$.

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. On the other
hand, a translation filter, $R_{t}^{L}$, is designed to look at a
larger search area to estimate the target's translation and recover
from any potential drifts. Another translation filter, $R_{t}^{S}$, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. In what follows, we
will detail the main idea behind the KCF.

@@

In what follows, we will detail two different types of features used
in {\it E}nKCF : (1) hand-crafted features (fHoG + color-naming) and
(2) deep convolutional features.

\textbf{{\it E}nKCF with Hand-Crafted Features} We, first, use two
conventional hand-crafted features, fHoG (shape)
\cite{felzenszwalb2010object} and color-naming (color)
\cite{li2014scale}. Figure \ref{fig:Filters} shows examples of these
features. This setup of the {\it E}nKCF is designed to perform
tracking on any embedded systems at $30$ fps, ones without GPUs.
\begin{figure}[!h]
\centering
\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
   \\[-3ex]
\subfloat[Small Area Translation Filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
\quad\subfloat[Large Area Translation Filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
\quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
\caption{Examples of three filters with hand-crafted features; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
\caption{The proposed conv224-VGGNet feature extraction in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ used an hanning window to avoid distortion caused by FFT operation whereas $R_{s}$ does not, to avoid target boundary information loss.}
\label{fig:Filters_CNN}
\end{figure}

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
We evaluate the performance of the proposed {\it E}nKCF tracker and
its variants using the object tracking benchmark
datasets. Particularly, we choose two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects.  We
first evaluate the performance of {\it E}nKCF with two hand-crafted
features, fHoG and color-naming.  With this tracker, we aim at
developing an object tracking algorithm that ``efficiently'' runs on
an embedded system, a drone, for example, in ``high speed,'' $\ge 30$
fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes,
e.g., abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset. To this end, we chose the OTB100 dataset that
contains the videos recorded from smart phones and typical cameras in
perspective view. Also, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets. Finally, we evaluate the
Deep{\it E}nKCF, {\it E}nKCF with deep features, on the UAV123 dataset
to observe how much gain we can achieve over hand-crafted features.

\textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
  E}nKCF is designed to address specific challenges in single target
tracking problem. Thus each of them should have different values for
the optimal parameters. For instance, the primary task of the
translation filter, $R_{t}^{L}$ is to estimate the translation of a
target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$. For the kernel of the Gaussian neighboring function, we
empirically found the optimal values of $\alpha$ as $0.7$, $0.6$, and
$0.9$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale
filter update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
ratio. Finally, the padding size for the correlation filters is tuned
to $3$ for $R_{t}^{L}$, $2.50$ for $R_{t}^{S}$, and $1$ for
$R_{s}$. For our particle filter implementation, we empirically set
the number of particles to $1000$ to balance the run-time performance
and accuracy. To keep the level of variance among the particles
reasonable, we performed the re-sampling only when the
\textit{efficient number of samples}, ($ \hat{N}_{eff} \approx
(\sum_{p=1}^{P}w_{p}^{2})^{-1} $), is lower than a pre-defined
threshold.

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate metrics to compare the performance of the proposed
algorithm with those of the state-of-the-art high speed tracking
algorithms. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high},
MOSSE \cite{bolme2010visual,henriques2015high}, and STC \cite{zhang2014fast} and ones in relatively
lower-speed ($\geq$50): SAMF \cite{li2014scale}, DSST
\cite{danelljan2014accurate}, Struck \cite{hare2012efficient}, MUSTER
\cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
results on the UAV123 dataset. {\it E}nKCF outperformed most of the
high-speed tracking methods by $3\%$-$15\%$ at 20 pixels
precision. Three algorithms, SAMF, DSST, and Struck did about 5\%
better than ours in accuracy, but 10-20 times slower. For the scale
adaptation, {\it E}nKCF did second best in terms of AUC for the
success rate plot. It outperformed other tracking methods in
high-speed by about $20\%$-$25\%$ in AUC. In addition, it performed
even better than those algorithms that are slow, but a slightly better
in precision. For example, for AUC, {\it E}nKCF outperformed Struck
and DSST by $5\%$ and $10\%$ while running at more than $10$ and $30$
times faster.

\begin{table*}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Results of running different combinations of the KCFs for
  UAV123 dataset. This table empirically supported the usefulness of
  combining multiple KCFs as long as the deployment order is optimal. The '$*$' represents
  sequential approach where multiple KCFs are run in the given order in every frame as in LCT \cite{ma2015long}.}
\label{table:Comparison_to_LCT}
\end{table*}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. This is primarily because
most of embedded systems come with an image acquisition pipeline, and
a tremendous amount of progresses on computer vision research has been
made for the past few decades. However, to successfully deploy a
computer vision algorithm on any existing embedded systems, a vision
algorithm needs to satisfy, at least, two criteria with the assumption
of reasonably good performance: minimal, manual intervention after
deployment and small footprint of consuming computational
resources. Kept these criteria in mind, to develop a single, target
tracking system, we propose an ensemble of the kernelized correlation
filters (KCF), we call {\it E}nKCF. This committee of KCFs is
specifically designed to address the scale-change and dynamic maneuver
of the target over frames. In particular, to guarantee a high-speed,
run-time performance, we deploy each of KCFs in turn, instead of
applying multiple KCFs on each frame. To minimize any potential drifts
between individual KCFs' transition, we developed a Bayes
filter. Experimental results showed that the performance of ours are,
on average, 70.10\% for precision at 20 pixels, 53.00\% for success
rate for OTB100 data, and 54.50\% and 40.2\% for UAV123 data. These
results showed that our method is better than existing ones over 5\%
on precision on 20 pixels and 10-20\% on AUC on average. Moreover our
implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
DCF (457 fps) for UAV123. To increase flexibility of the proposed {\it
  E}nKCF running on various single-board computers, particularly, ones
with GPUs, we explored different levels of deep features.
\end{abstract}

@@

\begin{figure*}[!h]
\centering
\begin{tabular}{cc}
\includegraphics[width=14.00cm]{./figures/Workflow_MKCF+PF.pdf}\\
\end{tabular}
\caption{The work-flow of the proposed single-target tracking
  algorithm, {\it E}nKCF. We show the first seven frames of tracking
  where the first frame is the initialization frame. Afterward, the
  order of deploying three KCFs is repeating.}
\label{Workflows}
\end{figure*}

One of the dominant frameworks for online, object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that a target location is given at the beginning
like any other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a form of the
circulant matrix \cite{henriques2015high}. One can optimally solve
this regression problem using a ridge regression in a closed
form. However, this solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, an object tracking pipeline based on the
correlation filter can run very efficiently and be even easily
implemented. In fact, an extension of a linear correlation filter, the
kernelized correlation filter with multi-channel features
\cite{henriques2015high} showed impressive object tracking results and
outperformed other state-of-the-art, online tracking algorithms in
terms of run-time and tracking accuracy. However, a vanilla form of
such an online tracker is prone to drift, and fails to track a target
over a long period of time \cite{henriques2015high}. This is primarily
due to the dilemma of stability-plasticity in updating appearance
model, where the appearance model will be overfitted to only the
images used to train, unless a compromise on the frequency of updating
the model is carefully implemented \cite{santner2010prost}. For
example, one may handle a target's scale variation by just
concatenating multiple correlation filters including KCF and running
them on each frame. Alternatively one could think of scanning the
region of interest (ROI) with a list of templates in predefined scale
ratios to find the target in appropriate scale
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
these approaches will drastically reduce run-time performance because
they are proposed to run multiple KCF on each frame.

Another way of handling the scale change for the correlation filter
based approach is to estimate a correct scale at a location where a
target highly likely appears \cite{zhang2014fast} -- estimate a
target's translation first and estimate a correct scale afterward. In
particular, Zhang and his colleagues use the MOSSE tracker to estimate
a target's translation. And then they attempted to update the scale of
the target by further analyzing image, sub-regions with high
confidence. This is based on an assumption that the scale of a target
would not change much over two consecutive frames. Similarly, Ma and
his colleagues used two KCFs to learn the translation and scale of a
target separately \cite{ma2015long}. In particular, a KCF is used to
learn the translation of the target and its background. Given this,
another KCF is used to learn the target area to estimate a new scale
of the target. However, because of running more than a KCF on each
frame, this method degrades its run-time performance (i.e., $\leq 50
fps$). Our method is motivated by this idea -- the idea of deploying
multiple KCFs to address the issues of single target tracking: scale
and translation, but in a more efficient way. To maximize run-time
performance and accuracy, instead of running them all together on
every frame, we deploy three KCFs in turn:
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). By doing so, our method aims at addressing a scale
change and estimate target's motion efficiently while maintaining or
increasing run-time performance. Figure \ref{Workflows} illustrates
the work-flow of the {\it E}nKCF.

The contribution of this paper is a novel, single-target tracking
algorithm running in a very high-speed, $\geq 300$ fps that deploys an
ensemble of KCFs, in turn, to more effectively address the scale
variance and the dynamic maneuver of a target while preserving
run-time performance as high as possible. We also developed a Bayes
filter to minimize any potential drifts while transiting one KCF to
another. In addition, we explore deep features with varying levels of
abstraction in the proposed {\it E}nKCF to improve tracking
performance and increase its flexibility being deployed on high-end,
single-board computer with GPUs.

@@

We propose a novel way of utilizing a multiple of the KCFs
\cite{henriques2015high} to effectively handle scale variations and
dynamic maneuvers of a target. To maintain or improve the run-time
performance of the original KCF (e.g., $\ge$ 300), we deploy three
KCFs in turn, instead of applying them on the same image frame
together. Each of these KCFs is designed to address specific
challenges: scale and translation. By alternating their deployments,
our algorithm will improve the performance of the original KCF while
preserving the efficient nature and small-footprint of the KCF
computation.

@@

Our approach is similar to that of \cite{ma2015long} in that more than
one KCF is used to address the challenges of single target
tracking. But ours is different from their approach because we do not
use those multiple KCFs together at every frame, but alternatively at
every $k$ frame. It intuitively makes sense to alternatively use
multiple KCFs with different purposes because the appearance of a
target does not change drastically over consecutive image frames. For
most case, even it looks the appearance changes, learning a
correlation filter over consecutive frames would not be much different
from the one learned using the image few or $k$ frames later. Figure
\ref{fig:Filters_Comparison} shows examples supporting this
observation.

\begin{comment}
Since Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high} on VOT15
challenge \footnote{\url{http://www.votchallenge.net/vot2015/}}, many
variation of KCF were investigated. For example, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is similar to that of \cite{ma2015long} in
that more than one KCF is used to address the challenges of single
target tracking. But ours is different from their approach because we
do not use those multiple KCFs together at every frame, but
alternatively at every $k$ frame. It intuitively makes sense to
alternatively use multiple KCFs with different purposes because the
appearance of a target does not change drastically over consecutive
image frames. For most case, even it looks the appearance changes,
learning a correlation filter over consecutive frames would not be
much different from the one learned using the image few or $k$ frames
later. Figure \ref{fig:Filters_Comparison} shows examples supporting
this observation.
\end{comment}

@@

The algorithm \ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF.
The order of running these three KCFs is important because each of
these filters aims at addressing different challenges. The
\textit{target+large background} translation filter, $R_{t}^{L}$, is
applied to the $i$th and $i$+$1$th image frames, another translation
filter, $R_{t}^{S}$ is applied to the $i$+$2$th and $i$+$3$th image
frames, and then the scale filter, $R_{s}$ is applied to the
$i$+$4$the image. This order repeats until the end of the image
frames. The translation filter, $R_{t}^{L}$, is intended to run right
after the scale filter, $R_s$, runs which is applied at every other
$i$+$4$ frames. We run these filters in this way because we want to
minimize any drifts that are likely to happen running only $R_{s}$. In
addition, the filter, $R_{t}^{S}$, is applied to every other two
frames before $R_{s}$ and right after two consecutive frames running
$R_{t}^{L}$. By repeating this order of learning KCFs, we can
integrate more discriminative shape features that cannot be learned
just by $R_{t}^{L}$. The filter, $R_{t}^{L}$, uses shape and color
information together to recover from any potential drifts -- drifts
could happen only looking the target's scale by the filter, $R_{s}$.

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides other translation filters
$R_{t}^{L}$ and $R_{t}^{S}$ with more focused ROIs about the target's
translation. On the other hand, a translation filter, $R_{t}^{L}$, is
designed to look at a larger search area to estimate the target's
translation and recover from any potential drifts. Another translation
filter, $R_{t}^{S}$, is designed to addresses the drawback of
$R_{t}^{L}$ that it may learn noisy shape features due to its large
search area. In what follows, we will detail the main idea behind the
KCF.

@@

In the following sections, we will detail two different types of
features used in {\it E}nKCF : (1) hand-crafted features (fHoG +
color-naming) and (2) deep convolutional features.

\textbf{{\it E}nKCF with Hand-Crafted Features} We, first, use two
conventional hand-crafted features, fHoG (shape)
\cite{felzenszwalb2010object} and color-naming (color)
\cite{li2014scale}. Figure \ref{fig:Filters} shows examples of these
features. This setup of the {\it E}nKCF is designed to perform
tracking on any embedded systems at $30$ fps, ones without GPUs.
\begin{figure}[!h]
\centering
\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
   \\[-3ex]
\subfloat[Small Area Translation Filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
\quad\subfloat[Large Area Translation Filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
\quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
\caption{Examples of three filters with hand-crafted features.}
\label{fig:Filters}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
\caption{The proposed conv224-VGGNet feature extraction in Deep{\it
    E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ used an hanning window to
  avoid distortion caused by FFT operation whereas $R_{s}$ does not,
  in order to avoid target boundary information loss.}
\label{fig:Filters_CNN}
\end{figure}

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
We evaluate, using the object tracking benchmark datasets, the
performance of the proposed algorithm {\it E}nKCF and its variants.
Particularly, we choose two publicly, available datasets:
OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects.  We
first evaluate the performance of {\it E}nKCF with two hand-crafted
features, fHoG and color-naming.  With this version, we would like to
have an object tracking algorithm that ``efficiently'' runs on an
embedded system, a drone, for example, in ``high speed,'' $\ge 30$
fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes,
e.g., abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset. To this end, we chose the OTB100 dataset that contains the
videos recorded from smart phones and typical cameras in perspective
view. Also, we tested the proposed algorithm on a temporally
down-sampled version of the UAV123 dataset, called UAV123$\_$10fps
dataset. What we would like to evaluate using this modified dataset is
how robust the proposed algorithm is to the drastic motions of camera
and targets. Finally, we evaluate the Deep{\it E}nKCF, {\it E}nKCF
with deep features, on the UAV123 dataset to observe how much gain we
can achieve over hand-crafted features.

\textbf{Finding Optimal Hyper-parameters} As each of three KCFs in
       {\it E}nKCF is designed to address specific challenges in
       single target tracking problem, the optimal parameters for
       individual KCFs should be different. We set the learning rates
       of individual filters, $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$
       differently as $0.020$, $0.020$ and $0.010$. For the kernel of
       the Gaussian neighboring function, we empirically found the
       optimal values of $\alpha$ as $0.7$, $0.6$, and $0.9$ for
       $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale filter
       update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
       ratio. The padding size for the correlation filters is tuned to
       $3$ for $R_{t}^{L}$, $2.50$ for $R_{t}^{S}$, and $1$ for
       $R_{s}$. For our particle filter implementation, we empirically
       set the number of particles to $1,000$ to balance the run-time
       performance and accuracy. To keep the level of variance among
       the particles reasonable, we performed the re-sampling only
       when the \textit{efficient number of samples}, ($ \hat{N}_{eff}
       \approx (\sum_{p=1}^{P}w_{p}^{2})^{-1} $), is lower than a
       pre-defined threshold.

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate to compare the performance of the proposed algorithm with
those of the state-of-the-art, online algorithms for high speed
tracking. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high}, MOSSE
\cite{bolme2010visual,henriques2015high}, and STC \cite{zhang2014fast}
and ones in relatively lower-speed ($\geq$50): SAMF
\cite{li2014scale}, DSST \cite{danelljan2014accurate}, Struck
\cite{hare2012efficient}, MUSTER \cite{hong2015multi}, TLD
\cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. Figure
\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset. {\it
  E}nKCF outperformed most of the high-speed tracking methods by
$3\%$-$15\%$ at 20 pixels precision. Three algorithms, SAMF, DSST, and
Struck did about 5\% better than ours in accuracy, but 10-20 times
slower. For the scale adaptation, {\it E}nKCF did second best in terms
of AUC for the success rate plot. It outperformed other tracking
methods in high-speed by about $20\%$-$25\%$ in AUC. In addition, it
performed even better than those algorithms that are slow, but a
slightly better in precision. For example, for AUC, {\it E}nKCF
outperformed Struck and DSST by $5\%$ and $10\%$ while running at more
than $10$ and $30$ times faster.

\begin{table*}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Results of running different combinations of the KCFs for
  UAV123 dataset.  The '$*$' represents
  sequential approach where multiple KCFs are run in the given order in every frame as in LCT \cite{ma2015long}.}
\label{table:Comparison_to_LCT}
\end{table*}
